A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-12-09 doc/review-acom/response-to-referees.tex

\item[2.] {\color{blue}
  In the abstract the Stokes operator is denoted as fourth-order operator.
This is unusual and in my opinion not the case (even if there is an
equivalence to a forth-order operator).}

We see how this could be confusing and have adjusted this phrasing.

\item[3.] {\color{blue} I would appreciate it if the following issue would be addressed in the
paper: under which weaker conditions (not analytic boundary, non-
simple eigenvalues) convergence of the discretization of the eigenvalues
can be proven. (Are there results concerning the convergence of the
eigenfunctions?)}

The question of addressing this problem under weaker assumptions of smoothness of the boundary
is a very interesting one. To the best of our knowledge, this
question hasn't even been addressed for the eigenvalues of the Laplacian.
We have a sketch of a proof of convergence for the eigenvalues and eigenfunctions
for the Laplace operator where we can show that the eigenvalues and eigenfunctions
converge at an algebraic rate (dependent on the smoothness of curves) for $C^{\ell}$,
with $\ell\geq 2$, boundaries. The procedure of using the Fredholm determinant as
stated does not work on Lipchitz boundaries, since the corresponding operators are
not second kind.

However, we feel that the discussion would be fairly technical and distract
from the main results of the paper --- demonstrating the use of Fredholm determinants
and second kind formulations for computing the Stokes operator eigenvalues and
eigenfunctions.  For this reason we feel that this analysis should be carried out in
a separate work and done for both the Laplace and Stokes cases.

We've included a sketch of the proof below.

The main estimate needed is to show that the error in computing
the Fredholm determinant at an eigenvalue of the Stokes operator
is directly proportional to the quadrature error for evaluating
the convolution of the integral kernel with the true null vector
of the integral operator with $k$ corresponding to that eigenvalue.
Based on the second-kind nature of the operator from $C^{m,\alpha} \to C^{m,\alpha}$
for $m<\ell$ and $\alpha>0$ (when the boundary is $C^{\ell}$) one can show
that the resulting null vector must be at least in $C^{m,\alpha}$.
The quadrature error using Kress quadratures converges algebraically
when both the boundary and density being approximated are $C^{m,\alpha}$.

\item[4.] {\color{blue} In the paper it is not explicitly mentioned that
  both presented boundary integral equations may have non-trivial null-spaces
  for certain $k$ with ${\rm Im}(k) < 0$. These $k$s correspond to the eigenvalues of some
  related eigenvalue problems in the exterior domain. It is possible that
  these $k$s are also be detected by the root search method and that these
  eigenvalues may be some of those “spurious eigenvalues too far from
  real-valued” which are blamed to be caused by “noisy numerical determinant
  evaluation” but are actually caused by the used boundary integral formulation.}

### 2019-12-09 doc/review-acom/response-to-referees.tex

The question of addressing this problem under weaker assumptions of smoothness of the boundary
is a very interesting one. To the best of our knowledge, this
question hasn't even been addressed for the eigenvalues of the Laplacian.
We have a sketch of a proof of convergence for the eigenvalues and eigenfunctions
for the Laplace operator where we can show that the eigenvalues and eigenfunctions
converge at an algebraic rate (dependent on the smoothness of curves) for $C^{\ell}$,
with $\ell\geq 2$, boundaries. The procedure of using the Fredholm determinant as
stated does not work on Lipchitz boundaries, since the corresponding operators are
not second kind.

However, we feel that the discussion would be fairly technical and distract
from the main results of the paper --- demonstrating the use of Fredholm determinants
and second kind formulations for computing the Stokes operator eigenvalues and
eigenfunctions.  For this reason we feel that this analysis should be carried out in
a separate work and done for both the Laplace and Stokes cases.

We've included a sketch of the proof below.

The main estimate needed is to show that the error in computing
the Fredholm determinant at an eigenvalue of the Stokes operator
is directly proportional to the quadrature error in 
evaluating the integral operator applied to the null vector (A proof of this result for the 
Laplace case is contained in~\cref{sec:appb}). 
Based on the second-kind nature of the operator from $C^{m,\alpha} \to C^{m,\alpha}$
for $m<\ell$ and $\alpha>0$ (when the boundary is $C^{\ell}$) one can show
that the resulting null vector must be at least in $C^{m,\alpha}$.
The quadrature error using Kress quadratures converges algebraically
when both the boundary and density being approximated are $C^{m,\alpha}$.

### 2019-12-09 doc/draft-01-stokes/appendix-b.tex
adding sketch of proof

\section{Proof of convergence for general case}
Let $T_{n}$ denote the space of trignometric polynomials
$\{ e^{-inx}, \ldots e^{inx} \}$. Let $K_{n}: T_{n} \to T_{n}$ 
denote a discretization of the Helmholtz double layer kernel
using kress quadrature. Let $\phi_{0}$ denote the null vector
of $I+ K$, and let $\psi_{0}$ denote the null vector
of $I+K^{\ast}$. 
Let $P_{n}$ denote the orthogonal 
projection operator from $L^{2} \to T_{n}$.
Let $P_{n,\phi_{0}^{\perp}}: T_{n} \to T_{n}$ denote the orthogonal
projection on to the orthogonal complement of $P_{n} \phi_{0}$.
Let $P_{n,\psi_{0}^{\perp}}: T_{n} \to T_{n}$ denote the
analogous operator for $\psi_{0}$.

@@

The operator $D_{n}$ is the restriction of $I_{n} + K_{n}$ 
as a map from $P_{n} \phi_{0}^{\perp}$ 
to $P_{n} \psi_{0}^{\perp}$. 
As $n \to \infty$, $D_{n}$ converges pointwise to the restriction
of $I + K: \phi_{0}^{\perp} \to R(I+K)$. Moreover, the collection
of operators $K_{n}$ are collectively compact, and hence their restrictions
are also collectively compact. 
Since the operator $I+K: \phi_{0}^{\perp} \to R(I+K)$ is an invertible
operator, by standard estimates, for $n$ large enough $D_{n}$ is also 
an invertible operator.

@@

>>>>

\section{Proof of convergence for general case}
Let $T_{n}$ denote the space of trignometric polynomials
$\{ e^{-inx}, \ldots e^{inx} \}$. 
Let $\mathcal{K}$ denote the Helmholtz double layer integral operator
given by
\begin{equation}
\mathcal{K}[\phi] = \frac{i}{2}\int_{\Gamma} k H_{1}^{1}(k|x-y|) \frac{(x-y)\cdot n(y)}{|x-y|} \phi(y) dS_{y} \,
\end{equation}
where $k$ the Helmholtz parameter is assumed to be a dirichlet eigenvalue of the simply connected
domain $\Omega$ whose boundary is given by $\Gamma$, and $H_{1}^{1}$ is the Hankel function
of the first kind of order $1$.
It is well known that if $\Gamma$ is of class $C^{\ell,\alpha}$, then the
integral operator $\mathcal{K}: C^{\ell-1,\alpha} \to C^{\ell-1,\alpha}$ is a compact operator.
Furthermore, as shown in Zhao and Barnett, at the simple Dirichlet eigenvalues of the operator
$I + \mathcal{K}$ is not invertible and has a one dimensional null-space. Let $\phi_{0}$ denote
the null vector. 
By Fredholm theory, the adjoint $I + \mathcal{K}^{\ast}$ also has a one-dimensional null space.
Let $\psi_{0}$ denote the null vector of $I+\mathcal{K}^{\ast}$.

Let $K_{n}: T_{n} \to T_{n}$ 
denote a discretization of $\mathcal{K}$ 
using kress quadrature. 
Let $P_{n}$ denote the orthogonal 
projection operator from $L^{2} \to T_{n}$.
Let $P_{n,\phi_{0}^{\perp}}: T_{n} \to T_{n}$ denote the orthogonal
projection on to the orthogonal complement of $P_{n} \phi_{0}$.
Let $P_{n,\psi_{0}^{\perp}}: T_{n} \to T_{n}$ denote the
analogous operator for $\psi_{0}$.

@@

The operator $D_{n}$ is the restriction of $I_{n} + K_{n}$ 
as a map from $P_{n} \phi_{0}^{\perp}$ 
to $P_{n} \psi_{0}^{\perp}$.
The following statement requires a more careful proof.
{\color{red} As $n \to \infty$, $D_{n}$ converges pointwise to the restriction
of $I + K: \phi_{0}^{\perp} \to R(I+K)$. Moreover, the collection
of operators $K_{n}$ are collectively compact, and hence their restrictions
are also collectively compact. 
Since the operator $I+K: \phi_{0}^{\perp} \to R(I+K)$ is an invertible
operator, by standard estimates, for $n$ large enough $D_{n}$ is also 
an invertible operator.}

@@

First, we observe that $D_{n}$ is the restriction of an operator in trace class
with a kernel whose leading order singularity is $r^{2} \log{r}$. 
Thus, $D_{n}$ is itself in trace class, and extending the proof of Bornemann to this case,
we observe that the discrete determinant of $D_{n}$ converges to the Fredholm determinant
of $D$ at a rate of at least $O(1/n)$. This in particular implies that
$\sup_{n} |\det{D_{n}}| <\infty$.
Using Cauchy-Schwarz, the quantities $A_{n}, C_{n}D_{n}^{-1}B_{n}$ are bounded by
$|(I_{n} + K_{n})\phi_{n}|$.
Combining these results together, we get that
\begin{equation}
\left| \det{\begin{bmatrix} A_{n} & B_{n} \\ C_{n} & D_{n} \end{bmatrix}} \right| \leq C |(I_{n} + K_{n})\phi_{n}|
\end{equation}
